{{< var titll >}}

### 2024-07-11 presentation.qmd
abc

```{r, echo=F, message=F, warning=F, results='hide'}
library(huxtable)
library(kableExtra)
#Sys.info()[['sysname']]=="Emscripten"
#ManifoldDestiny::wasmconload()
metad <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
md <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
laws_df1 <- ManifoldDestiny::eqdef$meql
laws_df2 <- ManifoldDestiny::eqdef$meqs
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/stylized.R'))
#source(paste0(rprojroot::find_rstudio_root_file(),'/script/r/simulations.r'))
#source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
modlat <- eqpar$meql
```

@@

:::: {.columns}
::: {.column width="50%"}
Case 1
:::
```{r, echo=F}
clr <- c("black","green","red","blue")
lego_hux_imp_i <- as_hux(towi[,1:3]) %>%
  set_text_color(5, 1:2, clr[1]) %>%
  set_background_color(1, 1:3, clr[2]) %>% 
  set_background_color(2, 1:3, clr[3]) %>%
  set_background_color(3, 1:3, clr[4]) %>%
  set_background_color(4, 2:3, clr[4]) %>%
  set_background_color(5, 3:3, clr[4]) %>%
  set_font_size(16)
lego_hux_imp_i
```

::: {.column width="50%"}
Case 2
:::
```{r, echo=F}
lego_hux_imp_ii <- as_hux(towii[,1:3]) %>%
  set_text_color(5, 1:2, clr[1]) %>%
  set_background_color(1, 1:3, clr[2]) %>% 
  set_background_color(2, 1:3, clr[3]) %>%
  set_background_color(3, 1:3, clr[4]) %>%
  set_background_color(4, 2:3, clr[4]) %>%
  set_background_color(5, 3:3, clr[4]) %>%
  set_font_size(16)

@@

```{r, echo=F}
ctone_sf <- 'Election results applying standard form on case I'
stfo_sel <- dplyr::select(pro_elc_ex1$sdfc[1:3,],P,S,T,U,V,x,y,zeta,alpha,lamda)
cou_tb <- c("Precinct","S","T","U","V","x","y",'$\\zeta$',"$\\alpha$","$\\lambda$")
kableExtra::kbl(format(stfo_sel,digits=4),caption=ctone_sf) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
```

@@

## {{< var sec1.un3 >}}
```{r, echo=F}
lego_hux_imp <- as_hux(matrix(c("S","T","U","V"), 2, 2)) %>%
  set_background_color(1:2, 1, "black") %>% 
  set_background_color(1:2, 2, "grey") %>% 
  set_text_color(1:2, 1:2, "red") %>% 
  set_all_borders(brdr(2, "solid", "black"))
lego_hux_imp %>% set_caption("")
```

@@

```{r, echo=F}
ctone_hf <- 'Election results applying hybrid form case I'
stfo_sel <- dplyr::select(pro_elc_ex1$sdfc[1:3,],P,S,T,U,V,g,h,Gamma,alpha,Omega)
kableExtra::kbl(format(stfo_sel,digits=4),caption=ctone_hf) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
```

@@

```{r, echo=F}
ctone_hf <- 'Election results applying hybrid form case II'
stfo_sel <- dplyr::select(pro_elc_ex2$sdfc[1:3,],P,S,T,U,V,g,h,Gamma,alpha,Omega)
kableExtra::kbl(format(stfo_sel,digits=4),caption=ctone_hf) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
```

@@

```{r, echo=F}
ctone_of <- 'Election results applying opposition form'
stfo_sel <- dplyr::select(pro_elc_ex1$sdfc[1:3,],P,S,T,U,V,n,m,xi,Omega, lamda)
kableExtra::kbl(format(stfo_sel,digits=4), caption=ctone_of) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::row_spec(1, bold = F)
```

@@

## {{< var sec3.un1 >}}

@@

@@

@@

## {{< var sec6.un1 >}}
## {{< var sec6.un2 >}}
## {{< var sec6.un3 >}}
## {{< var sec6.un4 >}}

@@

>>>>

```{r, echo=F, message=F, warning=F, results='hide'}
ManifoldDestiny::wasmconload()
library(huxtable)
library(kableExtra)
library(ManifoldDestiny)
laws_df1 <- ManifoldDestiny::eqdef$meql
laws_df2 <- ManifoldDestiny::eqdef$meqs
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/stylized.R'))
#source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
#source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
modlat <- eqpar$meql
```

@@

:::: {.columns}
::: {.column width="50%"}
:::
```{r, echo=F}
#| label: fig-1.1
#| fig-cap: "Case 1:"
clr <- c("black","green","red","blue")
lego_hux_imp_i <- as_hux(towi[,1:3]) %>%
  set_text_color(5, 1:2, clr[1]) %>%
  set_background_color(1, 1:3, clr[2]) %>% 
  set_background_color(2, 1:3, clr[3]) %>%
  set_background_color(3, 1:3, clr[4]) %>%
  set_background_color(4, 2:3, clr[4]) %>%
  set_background_color(5, 3:3, clr[4]) %>%
  set_font_size(16)
lego_hux_imp_i
```

::: {.column width="50%"}
:::
```{r, echo=F}
#| label: fig-1.2
#| fig-cap: "Case 2:"
lego_hux_imp_ii <- as_hux(towii[,1:3]) %>%
  set_text_color(5, 1:2, clr[1]) %>%
  set_background_color(1, 1:3, clr[2]) %>% 
  set_background_color(2, 1:3, clr[3]) %>%
  set_background_color(3, 1:3, clr[4]) %>%
  set_background_color(4, 2:3, clr[4]) %>%
  set_background_color(5, 3:3, clr[4]) %>%
  set_font_size(16)

@@

```{r, echo=F}
#| label: tbl-sfc1
#| tbl-cap: 'Election results applying standard form on case I'
stfo_sel <- dplyr::select(pro_elc_ex1$sdfc[1:3,],P,S,T,U,V,x,y,zeta,alpha,lamda)
cou_tb <- c("Precinct","S","T","U","V","x","y",'$\\zeta$',"$\\alpha$","$\\lambda$")
kableExtra::kbl(format(stfo_sel,digits=4)) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
```

@@

## {{< var sec1.un3 >}}
```{r, echo=F}
lego_hux_imp <- as_hux(matrix(c("S","V","T","U"), 2, 2)) %>%
  set_background_color(1:2, 1, "black") %>% 
  set_background_color(1:2, 2, "grey") %>% 
  set_text_color(1:2, 1:2, "red") %>% 
  set_all_borders(brdr(2, "solid", "black"))
lego_hux_imp %>% set_caption("")
```

@@

```{r, echo=F}
#| label: tbl-sfc2
#| tbl-cap: 'Election results applying hybrid form case I'
stfo_sel <- dplyr::select(pro_elc_ex1$sdfc[1:3,],P,S,T,U,V,g,h,Gamma,alpha,Omega)
kableExtra::kbl(format(stfo_sel,digits=4)) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
```

@@

```{r, echo=F}
#| label: tbl-hfc2
#| tbl-cap: 'Election results applying hybrid form case II'
stfo_sel <- dplyr::select(pro_elc_ex2$sdfc[1:3,],P,S,T,U,V,g,h,Gamma,alpha,Omega)
kableExtra::kbl(format(stfo_sel,digits=4)) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
```

@@

```{r, echo=F}
#| label: tbl-hfc3
#| tbl-cap: 'Election results applying hybrid form case II'
stfo_sel <- dplyr::select(pro_elc_ex1$sdfc[1:3,],P,S,T,U,V,n,m,xi,Omega, lamda)
kableExtra::kbl(format(stfo_sel,digits=4)) %>% kableExtra::kable_paper(full_width = F) %>% kableExtra::row_spec(1, bold = F)
```

@@

## {{< var sec3.un1 >}}
```{r}
#| echo: false
#| output: false
apps <- basc
```
{{< include tabpar.qmd >}}

@@

### Normal form
```{r}
#| echo: false
#| output: false
apps <- rigv[[1]]
```
{{< include tab.qmd >}}

### Hybrid
```{r}
#| echo: false
#| output: false
apps <- rigv[[2]]
```
{{< include tab.qmd >}}

### Opposition
```{r}
#| echo: false
#| output: false
apps <- rigv[[3]]
```
{{< include tab.qmd >}}

@@

** Abc | S-A **

@@

## {{< var sec6.un1 >}}
```{r}
#| echo: false
#| output: false
apps <- app1
```
{{< include tabpar.qmd >}}

## {{< var sec6.un2 >}}
```{r}
#| echo: false
#| output: false
apps <- app2
```
{{< include tabpar.qmd >}}

## {{< var sec6.un3 >}}
```{r}
#| echo: false
#| output: false
apps <- app2
```
{{< include tabpar.qmd >}}
## {{< var sec6.un4 >}}
```{r}
#| echo: false
#| output: false
apps <- app4
```
{{< include tabpar.qmd >}}

@@

```{r, echo=F, warning=F, message=F}
#kableExtra::kbl(concl_appps,col.names=cou_abc) %>% kableExtra::kable_classic_2(full_width = F) %>% kableExtra::row_spec(1, bold = F)
```
